\chapter{Potential Impact}
\label{chapter:impact}

%% ---------------------------------------------------------------
\section{How MASFE Builds on Current Research and Market Capabilities}
\label{sec:builds-on}
%% ---------------------------------------------------------------

Current state-of-the-art onboard processing SmallSats (e.g.\ Planet Dove, Satellogic Aleph-1) run fixed pipelines and downlink all derived data without adaptive prioritisation. NASA's MODIS products (MOD13A1, MOD11A1) deliver 1--3 day latency at 250--500\,m resolution from fixed polar orbit passes. MASFE builds on two pillars of existing work:

\begin{enumerate}
  \item \textbf{Dr.\ Gold's Cornell pre-symptomatic detection methodology}~\cite{gold-webinar1}: MASFE operationalises her spectral detection technique at satellite scale with an adaptive revisit mechanism triggered by the same EVI and thermal signatures she identified.
  \item \textbf{JPL's ASPEN/CASPER onboard scheduling research}~\cite{jpl-scheduling}: MASFE advances this paradigm with a belief-state MDP formulation where per-patch stress probability is the scheduling variable, enabling information-theoretic resource allocation that scales with scene content rather than a fixed timeline.
\end{enumerate}

%% ---------------------------------------------------------------
\section{Technical Variable Effects vs Traditional Methods}
\label{sec:technical-effects}
%% ---------------------------------------------------------------

Simulation over a 120-pass growing season (50 field patches, 7 disease events) confirms: \textbf{97\,\%} downlink reduction vs naive raw-dump baseline; \textbf{100\,\%} pathogen detection retention; \textbf{$<$90\,min} alert latency vs 1--3 days for ground processing; minimum battery SOC 86\,\% (floor 15\,\%). Full three-way comparison results are provided in Appendix~\ref{appendix:results}. MASFE additionally delivers a spatial resolution improvement from 250--500\,m (standard MODIS products) to \textbf{30\,m GSD} via the onboard Simera-class multispectral imager --- enabling field-patch-level management unavailable from any current operational system.

\medskip
\noindent\textbf{Farm-scale economic impact.} For a 500\,ha regenerative tomato operation, MASFE's targeted alerts reduce fungicide application from whole-field preventative (\$85/ha) to patch-only reactive (\$7/ha for affected patches, typically $\sim$12\,\% of area) --- saving approximately \$38{,}000 per season in chemical costs while preventing an estimated \$120{,}000 in yield loss from undetected late blight. This translates the macro \$220\,billion crop loss burden into a per-farm business case at the \$3--5/ha/year MASFE subscription price.

%% ---------------------------------------------------------------
\section{Concrete Examples, Scenarios, and Limitations}
\label{sec:scenarios}
%% ---------------------------------------------------------------

\subsection*{Scenario 1: Early blight detection on a regenerative cover-crop farm}

A regenerative farm operator running no-till cover-crop tomatoes receives a MASFE alert at 07:42 on day~14 of the season, identifying three field patches with CSC $>$ 0.55 --- fourteen days before visible symptoms would appear. Targeted fungicide application to those three patches only costs approximately 8\,\% of the chemical input of preventative whole-field treatment. Without MASFE, the farmer applies preventative fungicide across the entire field, contributing to the 8\,billion\,lb/year pesticide burden documented by Dr.\ Gold~\cite{gold-webinar1}. Estimated pesticide reduction: $>$85\,\% on this farm.

\subsection*{Scenario 2: Irrigation stress on an arid regenerative farm}

A thermal anomaly triggers MASFE Stage~2 over five patches in early morning before the ground station window. The alert is downlinked at 09:15, with OpenET ET data appended, and appears as a geo-tagged field-patch overlay in the farmer's Climate FieldView dashboard within 15 minutes of contact. The farmer receives a combined soil moisture proxy and water-use advisory two days before wilting symptoms would appear, preserving both yield and soil carbon stock integrity.

\subsection*{Regenerative agriculture applications beyond pathogen detection}

MASFE's adaptive architecture directly supports core regenerative practices beyond disease detection: (1) \textbf{cover crop phenology monitoring} via EVI time-series tracking through the full growing season, enabling optimised termination timing; (2) \textbf{soil carbon stock verification} for Verra VCS methodology VM0042 credit issuance, which requires continuous land condition monitoring that fixed-schedule satellites cannot provide; (3) \textbf{no-till adoption verification} via surface roughness proxies derivable from thermal emissivity patterns --- supporting the growing market for regenerative agriculture certification.

\subsection*{Limitations}

\begin{itemize}
  \item CSC accuracy degrades under $>$30\,\% cloud cover; cloud-screening preprocessing is required in the production pipeline. Current simulation injects $\sim$30\,\% cloud-obscured passes and sensor measurement noise, with FP rate held below the $\leq$15\,\% user requirement.
  \item Current simulation validated on synthetic MODIS proxy data. Real-sensor calibration (radiometric, atmospheric correction) is required for production deployment.
  \item MDP policy parameters were optimised for temperate/Mediterranean crop conditions; re-calibration is required for tropical growing seasons with distinct phenology patterns.
  \item Current TRL~3 --- hardware-in-the-loop demonstration on LEON4FT evaluation board is required before flight qualification.
\end{itemize}
