\chapter{Introduction}
\label{chapter:introduction}

%% ---------------------------------------------------------------
\section{Overview and Team}
\label{sec:overview}
%% ---------------------------------------------------------------

\textbf{Solution overview.}
MASFE (Multi-Algorithm Scheduling and Fusion Engine) is an Orbital Edge AI system that directly answers NASA's challenge objective: to \emph{``orchestrate existing land observation algorithms into an efficient, responsive onboard intelligence layer''}~\cite{nasa-challenge-brief}. A reinforcement-learning-inspired Markov Decision Process (MDP) scheduler runs on a radiation-tolerant LEON4FT CPU, dynamically allocating compute across two NASA algorithms---MODIS MOD13A1 (Enhanced Vegetation Index) and MOD11A1 (Land Surface Temperature)---fused onboard via an FPGA preprocessing stage into a per-field Crop Stress Composite (CSC). The satellite makes real-time, on-orbit decisions about where to sense, which algorithms to execute, and what to downlink, delivering sub-90-minute crop pathogen risk alerts while reducing unnecessary data downlink by 97\,\% compared to naive raw-dump acquisition. The system deploys as a hosted payload on a Loft Orbital YAM platform, integrating with the OpenET ground service~\cite{openet-api} for complete farmer-facing irrigation and disease advisory capability.

\medskip
\noindent\textbf{Team.}
[Your Name] is completing a Bachelor of Science in Aerospace Engineering at TU Delft, Faculty of Aerospace Engineering. Relevant coursework includes spacecraft systems engineering, attitude and orbit control systems (AOCS---the Kalman filter and MDP share the same Bayesian state estimation mathematical framework), mission analysis and design, and embedded flight software. The core technical challenge in MASFE---partitioning computation between an FPGA and a radiation-tolerant CPU under SWAP constraints---is a direct application of TU Delft aerospace systems engineering training. Market and domain evidence is drawn from primary sources including Dr.\ Katie Gold's Cornell University research presented at NASA Space-to-Soil Webinar~1~\cite{gold-webinar1} and Loft Orbital's deployment experience presented at Webinar~2~\cite{mytkowicz-webinar2}.

%% ---------------------------------------------------------------
\section{Summary of All Five Judging Criteria}
\label{sec:criteria-summary}
%% ---------------------------------------------------------------

Table~\ref{tab:criteria} provides a condensed mapping of MASFE to all five judging criteria, as required by the submission guidelines.

\begin{table}[htb]
  \centering
  \caption{MASFE response to all five NASA Space-to-Soil judging criteria.}
  \label{tab:criteria}
  \small
  \begin{tabularx}{\textwidth}{p{2.8cm}X}
    \toprule
    \textbf{Criterion} & \textbf{How MASFE addresses it} \\
    \midrule
    \textbf{Creativity}
      & Novel two-stage MDP orchestration policy --- no current SmallSat uses MDP-class scheduling to jointly optimise algorithm selection, compute duty-cycling, and downlink priority in real time. Full stack named: FPGA $\rightarrow$ LEON4FT CPU $\rightarrow$ priority queue $\rightarrow$ Loft Orbital ground network $\rightarrow$ OpenET API $\rightarrow$ farmer dashboard. \\
    \addlinespace
    \textbf{Technical Feasibility}
      & Formal user requirements ($\leq$90\,min latency, 30\,m GSD, FP rate $\leq$15\,\%). Quantitative SWAP budget: peak 9.6\,W (budget $\leq$14\,W), LEON4FT 92.5\,\% compute utilisation, minimum battery SOC 86\,\% (floor 15\,\%), 97\,\% downlink reduction. All values from real component datasheets. \\
    \addlinespace
    \textbf{Impact}
      & 97\,\% downlink reduction vs raw baseline; 100\,\% science retention; sub-90-min pathogen alerts vs 1--3 day ground processing. Early detection enables targeted fungicide application against the 8\,billion\,lb/year global pesticide burden~\cite{gold-webinar1}. Addresses the \$220\,billion annual crop loss burden. \\
    \addlinespace
    \textbf{Business Model}
      & Market gap: no sub-day adaptive pathogen alert at $<$\$5/ha/year exists. Three paying markets: precision agriculture SaaS, carbon credit MRV (Verra registry), crop insurance underwriting. MVP TRL roadmap: simulation (TRL~3, now) $\rightarrow$ AIST TRL~4 hardware demo $\rightarrow$ Loft Orbital hosted payload pilot. MDP engine is domain-agnostic --- generalises to wildfire, flood, urban EO. \\
    \addlinespace
    \textbf{Presentation}
      & Paper follows required outline with requirements tracing to architecture to SWAP budget to impact metrics. Code submission demonstrates two-stage MDP scheduling on MODIS proxy data with quantified outputs. Architecture diagram and SWAP budget table included. \\
    \bottomrule
  \end{tabularx}
\end{table}
